---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Assignment 1: Reliability and tools for reproducible data science {#assignment1}

The purpose of this assignment is to present estimates of reliability of measures collected in the physiology lab. A second purpose is to use tools for reproducible data science. The report that you are expected to hand in therefore has some strict requirements in its format (see [assignment description](https://dhammarstrom.github.io/quant-methods-workshops/assignment-1.html)). The assignment is a group assignment and at least three students are expected to contribute to each report.

## Elements of the report

**Importantly, the report should contain:**

-   At least one table (created from your data)
-   At least one figure (created from your data), and
-   data presented in the text.
-   The report should use a bibliography file to manage references.

## **Starten av rapport**

```{r}
#| code-fold: true
#| message: false

library(readxl)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(magrittr)
library(gt)
df <- read_xlsx("data/o2-test.xlsx")

```



### Tabell over o2-tester med utvalgt data
```{r}
#| code-fold: true

df %>% 
  select(id, 
         age, 
         weight,
         w.max, 
         vo2.max, 
         hr.max, 
         la.max, 
         borg.max) %>% 
  mutate(rel.vo2max = vo2.max / weight) %>% 
  mutate(w.max.kg = w.max / weight) %>% 
  arrange(w.max) %>% 
  gt(auto_align = TRUE) %>% 
  fmt_number(decimals = 1)
    
  



```


### Figur fra o2-test


```{r}
#| code-fold: true

 ggplot(data = df, aes(x = vo2.max, y = w.max)) +
   geom_point()



```

